Exploration

### 2018-03-14 exploration.Rmd
enforce plot limits

## Observed datasets
The simulated species *S* is sampled appropriately in order to fit each SDM model. The observed datasets,*O*, may be random or intentionally biased to mimic common issues with empirical data. The realized simulated data generated above (`d` and its abundance summary `N_sim`) are the underlying true distribution. The samples will be drawn from occupied cells in the final time steps where the species is approximately at equilibrium.
```{r O_setup}
O_n <- list(Mx=500, CA=20, IPM=20) # number of cells in sample
O_yr <- list(Mx=tmax, CA=(tmax-10):tmax, IPM=tmax) # years to sample from
P.i <- which(lam.df$Surv.S > 0) # presences: surviving individuals > seedlings
n_sim <- 20
```

@@

  xx <- tibble(size=seq(U.f$lo, U.f$hi, length.out=100), 

@@

  xxx <- seq(0, U.f$hi*.5, length.out=100)

@@

    plot(surv~size, data=z.t, ylim=c(0,1), pch=20, col=pt.col,

@@

    plot(sizeNext~size, data=z.t, pch=20, col=pt.col, ylim=c(U$lo,U$hi),

@@

    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=pt.col,

@@

    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=pt.col, 

>>>>

## Observed datasets
The simulated species *S* is sampled appropriately in order to fit each SDM model. The observed datasets,*O*, may be random or intentionally biased to mimic common issues with empirical data. The realized simulated data generated above (`d` and its abundance summary `N_sim`) are the underlying true distribution. The samples will be drawn from occupied cells in the final time steps where the species is approximately at equilibrium.
```{r O_setup}
O_n <- list(Mx=500, CA=20, IPM=20) # number of cells in sample
O_yr <- list(Mx=tmax, CA=(tmax-10):tmax, IPM=tmax) # years to sample from
P.i <- which(lam.df$Surv.S > 0) # presences: surviving individuals > seedlings
n_sim <- 15
```

@@

  xx <- tibble(size=seq(U$lo, U$hi, length.out=100), 

@@

  xxx <- seq(0, U$hi*.5, length.out=100)

@@

    plot(z.t$surv~z.t$size, ylim=c(0,1), pch=20, col=pt.col, xlim=c(U$lo, U$hi),

@@

    plot(z.t$sizeNext~z.t$size, pch=20, col=pt.col, ylim=c(U$lo,U$hi),
         xlim=c(U$lo, U$hi),

@@

    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=pt.col, xlim=c(U$lo, U$hi),

@@

    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=pt.col, xlim=c(U$lo, U$hi),
